Effects of sexual selection on non-sexual fitness components: a meta-analysis

### 2018-05-28 meta_analysis_sexual_selection_pop_fitness.Rmd
Bayesian plots for Hedges' g and lnCVR

```{r, warning=FALSE, message=FALSE, results='hide'}
library(pander)
library(tidyr)
library(compute.es)
library(metafor)
library(plyr)
library(dplyr)
library(lme4)
library(forestplot)
library(ggplot2)
library(ggthemes)
library(kableExtra)
library(ggrepel)
library(reshape2)
library(RColorBrewer)
library(ggridges)
source("Vdodge_function.R") # nice function for ggplot
```

@@

Outcome_and_sex %>% pander(split.cell = 40, split.table = Inf)

@@

```{r, fig.height=18, fig.width=12}
# Run standard random effects model
# forest.model <- rma.mv(g, var.g, 
#                        mods = ~ 1 + Sex * Environment + Taxon,
#                        random = list(~ 1 | Study.ID, 
#                                        ~ 1 | Outcome),
#                        method = "REML", 
#                        data = prelim.data)
# 
# # Obtain residuals
# resstandards <- (rstandard.rma.mv(forest.model, 
#                                    type="response"))
# 
# # Obtain grand mean effect size    <- ADDED BY LUKE
# grand.mean <- as.numeric(forest.model$b)
# 
# # Create new df with residuals replacing raw
# df.forest.model <- prelim.data                     # <- Luke says: you could just use prelim.data itself, not the residuals?
# df.forest.model$g <- resstandards$resid + grand.mean   # <- ADDED BY LUKE
# df.forest.model$sei <- resstandards$se

@@

# define upper and lower bounds
prelim.data$lowerci <- prelim.data$g - 1.96*(sqrt(prelim.data$var.g))
prelim.data$upperci <- prelim.data$g + 1.96*(sqrt(prelim.data$var.g))
# 
# # Get author and year in one
# short.author.names <- data.frame(long = prelim.data$Authors %>% unique(),
#                                  short = prelim.data$Authors %>% unique() %>% 
#   as.character() %>% 
#   strsplit(split = ",") %>% 
#   sapply(FUN=function(x) x[1])) %>%
#   left_join(prelim.data %>% select(Authors, Year) %>% distinct(), by = c("long" = "Authors")) %>%
#   mutate(suffix = "")
# 
# # Sometimes there are multiple papers with the same first author from teh same year. Name these 2010a, 2010b etc
# dups <- with(short.author.names, table(short, Year)) %>% melt()
# dups <- dups[dups$value > 1, ]
# for(i in 1:nrow(dups)){
#   short.author.names$suffix[
#     short.author.names$short == dups$short[i] &
#       short.author.names$Year == dups$Year[i]] <- letters[1:dups$value[i]]
# }
# 
# # Add the AuthorYear column to the dataframe of effect sizes
# short.author.names <- short.author.names %>%
#   mutate(AuthorYear = paste(short, " ", Year, suffix, sep="")) %>%
#   select(long, AuthorYear)
# prelim.data <- prelim.data %>% 
#   left_join(short.author.names, by = c("Authors" = "long")) 
library(ggthemes)
#Generate a plot
p.meta <- prelim.data %>% 
  mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female")) %>%

@@

<!-- ###Quantitative summary using bootstrapped means -->

<!-- We can obtain a bootstrap weighted mean for the entire dataset. Although this does not take into account any moderator variables it does provide a rough guide on where most of the datapoints sit:  -->

<!-- ```{r} -->
<!-- #Run function -->
<!-- get.CIs.for.weighted.mean <- function(x, weights){ -->
<!--   total.resamples <- 10000 -->
<!--   num.chunks <- ceiling(length(x)*total.resamples / 10^7) # To be nice to RAM, let's keep these to ten million or less  -->
<!--   if(num.chunks == 1){ -->
<!--     rand <- sample(length(x), length(x)*total.resamples, replace = TRUE) -->
<!--     resampled.weighted.means <- data.frame(x = x[rand], w = weights[rand], replicate = rep(1:total.resamples, each = length(x))) %>%  -->
<!--       group_by(replicate) %>%  -->
<!--       summarise(w.mean = weighted.mean(x, w)) %>% .$w.mean -->
<!--   } -->

<!--   else{ -->
<!--     resampled.weighted.means <- vector(mode = "list", length = 0) -->
<!--     number.of.resamples <- floor(total.resamples/num.chunks) -->
<!--     final.chunk.size <- total.resamples - number.of.resamples * (num.chunks-1) -->
<!--     for(i in 1:num.chunks){ -->
<!--       if(i == num.chunks) number.of.resamples <- final.chunk.size -->
<!--       rand <- sample(length(x), length(x) * number.of.resamples, replace = TRUE) -->
<!--       resampled.weighted.means[[i]] <- data.frame(x = x[rand], w = weights[rand], replicate = rep(1:number.of.resamples, each = length(x))) %>%  -->
<!--         group_by(replicate) %>%  -->
<!--         summarise(w.mean = weighted.mean(x, w)) %>% .$w.mean -->
<!--     } -->
<!--     resampled.weighted.means <- unlist(resampled.weighted.means) -->
<!--   } -->

<!--   data.frame(w.mean = median(resampled.weighted.means), -->
<!--              lowerCI = quantile(resampled.weighted.means, probs = 0.025) %>% as.numeric(), -->
<!--              upperCI = quantile(resampled.weighted.means, probs = 0.975) %>% as.numeric()) -->
<!-- } -->

<!-- #Get weights -->
<!-- prelim.data$Standard.weights <- (1/prelim.data$var.g) -->

<!-- #Run function with weights -->
<!-- get.CIs.for.weighted.mean(prelim.data$g, prelim.data$Standard.weights) %>% pander() -->
<!-- ``` -->

@@

<!-- Check the results on a plot -->
<!-- ```{r} -->
<!-- pd <- position_dodgev(height = .7) -->
<!-- outcome.frame %>% ggplot(aes(x = b, y= Outcome)) +  -->
<!--   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") +  -->
<!--   geom_errorbarh(aes(xmin = ci.lb,  -->
<!--                      xmax = ci.ub), height = 0, position = pd, show.legend = F) + -->
<!--   geom_point(position = pd, color = "grey20") +  -->
<!--   ylab("Outcome\n")+ -->
<!--   xlab("\nEffect Size (Hedges g)")+ -->
<!--   xlim(-2.5, 2.5)+ -->
<!--   ggtitle('Standard Random Effects Model') -->
<!-- ``` -->

@@

<!-- >The following documents how I could run individual models for each outcome or outcome.class of interest and then plot them. This may be good to add to the above forest plot (in the form of a polygon; how many studies report their estimates) but at the same time, it just adds results from different subsetted models rather than one combined one (as we use when investigating sex and environment) -->

<!-- > Nice idea, but I think the correct way to do this is to fit Outcome.class as a moderator, and then use predict() to find the average effect size within each of the 3 levels, as you have done below. I coded something below, but it's wrong: -->

<!-- ```{r} -->
<!-- model.outcome.class <- rma(g, var.g, -->
<!--                            mods = ~ Outcome.Class,  -->
<!--                            method = "REML",  -->
<!--                            intercept = TRUE,  -->
<!--                            data = prelim.data) -->

<!-- # Get the intercept (i.e. the grand mean for 'ambiguous', and the effects for the others) -->
<!-- mod.table <- do.call("cbind", model.outcome.class[names(model.outcome.class) %in% c("b", "ci.lb", "ci.ub")]) -->

<!-- data.frame(Outcome.class = c("Ambiguous", "Direct", "Indirect"), -->
<!--            mod.table) %>% -->
<!--   ggplot(aes(y = Outcome.class, x = V1))  + -->
<!--   geom_vline(xintercept = 0, linetype = 2) + -->
<!--   geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), height=0) + -->
<!--   geom_point() +  -->
<!--   xlab("Effect size and 95% CIs") -->
<!-- ``` -->

<!-- There is not really enough direct outcomes to analyse by itself so hence we combine with indirect later -->
<!-- ```{r} -->
<!-- #Ambiguous outcomes -->

<!-- model.Ambiguous <- rma(g, var.g, -->
<!--                        mods = ~ 1,  -->
<!--                        method = "REML",  -->
<!--                        subset = (Outcome.Class == "Ambiguous"),  -->
<!--                        intercept = TRUE,  -->
<!--                        data = prelim.data) -->

<!-- summary(model.Ambiguous) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- #Indirect outcomes -->

<!-- model.Indirect <- rma(g, var.g, mods = ~ 1, method = "REML", subset = (Outcome.Class == "Indirect"), intercept = T ,data = prelim.data) -->

<!-- summary(model.Indirect) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- #Direct outcomes -->

<!-- model.Direct <- rma(g, var.g, mods = ~ 1, method = "REML", subset = (Outcome.Class == "Direct"), data = prelim.data) -->

<!-- summary(model.Direct) -->
<!-- ``` -->

<!-- Now let's combine into a data frame and plot. The following plot could then be added to the large forest plot as summary polygons or summary points with error bars.  -->

<!-- ```{r} -->
<!-- #Data frame -->
<!-- Outcome.category <- c('Ambiguous', 'Indirect', 'Direct') -->
<!-- Estimate <- c(model.Ambiguous$b, model.Indirect$b, model.Direct$b) -->
<!-- l.ci <- c(model.Ambiguous$ci.lb, model.Indirect$ci.lb, model.Direct$ci.lb) -->
<!-- u.ci <- c(model.Ambiguous$ci.ub, model.Indirect$ci.ub, model.Direct$ci.ub) -->
<!-- data.1 <- data.frame(Outcome.category, Estimate, l.ci, u.ci) -->

<!-- #plot -->

<!-- data.1 %>% ggplot(aes(x = Estimate, y= Outcome.category)) +  -->
<!--   geom_point() + -->
<!--   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") +  -->
<!--   geom_errorbarh(aes(xmin = l.ci, xmax = u.ci), height = 0, size=1) + -->
<!--   ylab("Outcome Category")+ -->
<!--   xlab("Effect Size")+ -->
<!--   xlim(-.2, .5)+ -->
<!--   ggtitle('Meta-Analysis Results') -->
<!-- ``` -->

<!-- From the previous forest plot and models we see that overall sexual selection is beneficial towards population fitness. Although this is heavily modulated by the individual outcome and the outcome class. We explore heterogeneity in more depth later in this document.  -->

@@

<input type=button class=hideshow></input>
```{r}
model.preliminary <- rma.mv(g, var.g, 
                         mods = ~ 1 + Sex * Environment + Taxon + Outcome.Class + Generations + Blinding, # << ----- Add big model, then cull predictors to this one
                         random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                         method = "REML", 
                         data = prelim.data)

summary(model.preliminary)
```
<br></br>

@@

summary(model.complete) 
```

@@

We can run a bayesian model using the brms package. The model has the same moderators as the REML approach used above. 
```{r, warning=FALSE, message = FALSE}
library(rstan) #Note that installation requires some effort
library(brms) 
library(backports) #seems to be a dependency
#devtools::install_github("mvuorre/brmstools")
library(brmstools) 
```

```{r, warning = FALSE, results='hide', message=FALSE}
#Use brm to create a model similar to the one used in the REML approach. 
#Use brm to create a model similar to the one used in the REML approach. 
meta.brms <- brm(g| se(sqrt(var.g), sigma = TRUE)  ~ 1 + Sex * Environment #response is Hedges' g and the standard error associated with it (sqrt(var.g)) with sex, environment and their interaction as moderators
                + (1|Study.ID) #group level effect #1
                + (1|Outcome), #group level effect #2 (unrelated/crossed) with #1
                family = "gaussian", #default
                seed = 1,
                cores = 4, chains = 4, iter = 4000, #Run 4 chains in parrallel for 4000 iterations (2000 are burn in)
                control = list(adapt_delta = 0.99),
                data = restricted.data)
```

```{r}
summary(meta.brms)
```

Plot summary of the model estimates
```{r}
plot(meta.brms)
```

We can also obtain marginal effects plots

> Are these like the predictions?

```{r}
marginaleffects <- marginal_effects(meta.brms)
```

Obtain fitted values: **Note that the fitted values obtained here have much smaller error than the predict values, which blow out**

```{r}
#obtain average variance of each group in the prediction
av.var.g <- as.numeric(c(restricted.data %>% filter (Sex == 'M' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
              restricted.data %>% filter (Sex == 'B' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
              restricted.data %>% filter (Sex == 'F' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
              restricted.data %>% filter (Sex == 'M' & Environment == "Stressed") %>% summarise(mean = mean(var.g)),
              restricted.data %>% filter (Sex == 'B' & Environment == "Stressed") %>% summarise(mean = mean(var.g)),
              restricted.data %>% filter (Sex == 'F' & Environment == "Stressed") %>% summarise(mean = mean(var.g))))

#Expand grid for environment and sex
brms.newdata <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
                           Environment = c("Unstressed", "Stressed")))
#Add variance
brms.newdata$var.g <- av.var.g

#Add predictions
brms.predict <- fitted(meta.brms, newdata = brms.newdata, re_formula = NA)
brms.predict <- as.data.frame(brms.predict)
brms.predictions <- data.frame(brms.newdata$Sex, brms.newdata$Environment, brms.predict$Estimate, brms.predict$Est.Error, brms.predict$Q2.5, brms.predict$Q97.5)

#Add sample size 
brms.predictions$n <- as.numeric(predictions.complete2$n)

#Name columns
colnames(brms.predictions) <- c("Sex", "Environment", "Estimate", "Error", "LCI", "UCI", "n")
```

Plot results for brms prediction using the same ggplot code as for the metafor model predictions

```{r, fig.height=6, fig.width = 6}
EnvSex.metaanalysis.brms <- brms.predictions %>% 
      mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female")) %>%
  ggplot(aes(x = Estimate, y= Environment, fill = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
  geom_errorbarh(aes(xmin = brms.predictions$LCI, 
                     xmax = brms.predictions$UCI,
                     color = Sex), height = 0, position = pd, show.legend = F) +
  geom_point(aes(size=n), position = pd, shape=21, color = "grey20") + 
  scale_size(guide = 'none')+
  ylab("Environment\n")+
  xlab("\nEffect Size (Hedges' g)")+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")+
  guides(fill = guide_legend(reverse=T, override.aes = list(size = 3)))+
  scale_x_continuous(limits = c(-0.2, 1), breaks = c(-0.2, 0, 0.2, 0.4, 0.6, 0.8, 1))+

EnvSex.metaanalysis.brms
```
<br></br>
**Figure X** Bayesian fitted values for effect size using a comprable model to the one used in the REML approach

@@

```{r}
#Obtain posterior fitted values and transform
posterior_fit <- data.frame(t(posterior_linpred(meta.brms, newdata = brms.newdata, re_formula = NA)))

#Add columns for Environment and Sex
posterior_fit$Sex <- c("Male", "Both", "Female", "Male", "Both", "Female")
posterior_fit$Environment <- c("Benign", "Benign", "Benign", "Stressful", "Stressful", "Stressful")

#Clean up dataframe
posterior_fit <- melt(posterior_fit, id = c("Sex", "Environment"))
posterior_fit$variable <- NULL
```

@@

pd <- position_dodgev(height = 0.3)
posterior.plot <- posterior_fit %>% ggplot()+
  geom_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.4, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F)+
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
    ylab("Environment")+
  xlab("\nEffect Size (Hedges' g)")+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")+
  scale_x_continuous(limits = c(-0.5, 1.2), breaks = c(-1, -.5, 0, 0.5, 1))+

@@

# svg("figures/both_plot.svg", width=5.5, height=5.5)
# both.plots
# dev.off()
# 
# pdf("figures/both_plot.pdf",  width = 5.5, height = 5.5)
# both.plots
# dev.off()
```
<br></br>
**Figure X** Posterior fitted values for Hedges' g using the same model as above

@@

<!-- Furthermore, we can obtain estimates of the intra-class correlation (ICC) within a study via:  -->
<!-- ```{r} -->
<!-- round(model.complete2$sigma2[1] / sum(model.complete2$sigma2), 3) -->
<!-- ``` -->

<!-- This means that within a study, between different outcomes, there is a correlation of 26.2 % (low-medium). This justifies including outcome as a level, as without it we would be assuming ICC = 1. We can also gain an estimate of the total heterogeniety, as the sum of the sigma componenets:  -->
<!-- ```{r} -->
<!-- round(sum(model.complete2$sigma2), 3) -->
<!-- ``` -->

<!-- #### Multilevel model using metafors alternative random effect structure  -->

<!-- > This inner, outer factor stuff from the metafor package is a bit strange. There is a description in ``?rma.mv()`` but still unsure how it differs from the above model. It seems that it is useful to breakdown variance-covariance matrix but unsure how that would benefit our analysis. -->

<!-- ```{r} -->
<!-- #Just to check, how about with outcome as the inner factor  -->
<!-- model.complete2.2 <- rma.mv(g, var.g, mods = ~ 1 + Sex + Environment + Sex:Environment, random = ~ factor(Outcome) | Study.ID, method = "REML", data = restricted.data) -->

<!-- summary(model.complete2.2) -->

<!-- #Now with a slightly different structure (HCS) -->

<!-- model.complete2.3 <- rma.mv(g, var.g, mods = ~ 1 + Sex + Environment + Sex:Environment, random = ~ Outcome | Study.ID, struct = "HCS", method = "REML", data = restricted.data) -->

<!-- summary(model.complete2.3) -->
<!-- ``` -->

<!-- ```{r, fig.height= 7, fig.width=10} -->
<!-- #Generate predictions without taxon -->

<!-- get.predictions.complete2 <- function(newdata){ -->
<!--   B<-0; F<-0; Stressed<-0; interaction1<-0; interaction2<-0; interaction3<-0 -->
<!--   if(newdata[1] == "B") B<-1  -->
<!--   if(newdata[1] == "F") F<-1  -->
<!--   if(newdata[2] == "Stressed") Unstressed<-1 -->
<!--   if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1 -->
<!--   if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1 -->

<!--   predict(model.complete2.2, newmods=c(B, F, Stressed, interaction1=interaction1, interaction2=interaction2)) -->
<!-- } -->
<!-- # Get the predictions for each combination of moderators -->
<!-- predictions.complete2 <- as.data.frame(expand.grid(Sex = c("M", "B", "F"), -->
<!--                            Environment = c("Unstressed", "Stressed"))) -->
<!-- predictions.complete2 <- cbind(predictions.complete2, do.call("rbind", apply(predictions.complete2, 1, get.predictions.complete2))) %>% -->
<!--   select(Sex, Environment, pred, se, ci.lb, ci.ub)  -->
<!-- for(i in 3:6) predictions.complete2[,i] <- unlist(predictions.complete2[,i]) -->

<!-- #And plot the results -->

<!-- pd <- position_dodgev(height = .3) -->
<!-- predictions.complete2 %>% ggplot(aes(x = pred, y= Environment, colour = Sex)) +  -->
<!--   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") +  -->
<!--   geom_errorbarh(aes(xmin = predictions.complete2$ci.lb, xmax = predictions.complete2$ci.ub), height = 0, position = pd) + -->
<!--   geom_point(position = pd) +  -->
<!--   ylab("Environment")+ -->
<!--   xlab("Effect Size (Hedges g)")+ -->
<!--   xlim(-.75, .75)+ -->
<!--   ggtitle('Effects of Sex, Stress \non Population Fitness (OUTCOME = INNER FACTOR)') -->
<!-- ``` -->

@@

```{r}
#Calculate lnCVr and var.lnCVr
#for lnCVR
prelim.data2$lnCVr <- Calc.lnCVR(prelim.data2$mean.low, prelim.data2$sd.low, prelim.data2$n.low, prelim.data2$mean.high, prelim.data2$sd.high, prelim.data2$n.high)

#for variance in lnCVR
prelim.data2$var.lnCVr <- Calc.var.lnCVR(prelim.data2$mean.low, prelim.data2$sd.low, prelim.data2$n.low, prelim.data2$mean.high, prelim.data2$sd.high, prelim.data2$n.high, Equal.E.C.Corr=F)

prelim.data2 <- prelim.data2 %>% drop_na(lnCVr)
```

<!-- #Run simple models subsetted for each environment/sex (this is perhaps a clunky way so we also use predictions shown below) -->

<!-- # For stressed environment and females -->
<!-- varSF <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Stressed" & Sex == "F")) -->

<!-- # For stressed environment and females -->
<!-- varSM <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Stressed" & Sex == "M")) -->

<!-- # For stressed environment and females -->
<!-- varSB <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~ 1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Stressed" & Sex == "B")) -->

<!-- #For Benign environment and females -->
<!-- varUF<- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Unstressed" & Sex == "F")) -->

<!-- #For Benign environment and males -->
<!-- varUM<- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Unstressed" & Sex == "M")) -->

<!-- #For Benign environment and both -->
<!-- varUB <- rma.mv(lnCVr, var.lnCVr, data = prelim.data2, mods = ~1, random = ~ 1 | Study.ID/Outcome, subset = (Environment == "Unstressed" & Sex == "B")) -->

<!-- #Create dataframe of estimates and confidence intervals -->
<!-- lnCVR <- c(varSF$b, varSM$b, varSB$b, varUF$b, varUM$b, varUB$b) -->
<!-- l.ci <- c(varSF$ci.lb, varSM$ci.lb, varSB$ci.lb, varUF$ci.lb, varUM$ci.lb, varUB$ci.lb) -->
<!-- u.ci <- c(varSF$ci.ub, varSM$ci.ub, varSB$ci.ub, varUF$ci.ub, varUM$ci.ub, varUB$ci.ub) -->
<!-- Environment <- c("Stressed", "Stressed", "Stressed", "Unstressed", "Unstressed", "Unstressed") -->
<!-- Sex <- c("Female", "Male", "Both", "Female", "Male", "Both") -->
<!-- k <- c(varSF$k, varSM$k, varSB$k, varUF$k, varUM$k, varUB$k) -->

<!-- var.data <- data.frame(lnCVR, l.ci, u.ci, Environment, Sex, k) -->

<!-- #Releveling the factors to make sure it aligns with other formatted graphs -->
<!-- var.data$Environment <- var.data$Environment %>% factor %>% relevel(ref="Unstressed") -->
<!-- var.data$Sex <- var.data$Sex %>% factor %>% relevel(ref="Male") -->

<!-- #Plot subseted model estimates -->

<!-- var.data %>% ggplot(aes(x=lnCVR, y = Environment, colour = Sex))+ -->
<!--   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + -->
<!--   geom_errorbarh(aes(xmin = l.ci, xmax = u.ci), height = 0, position = pd) + -->
<!--   geom_point(position = pd) + -->
<!--   ylab("Environment")+ -->
<!--   xlab("lnCVR")+ -->
<!--   xlim(-.75, .75)+ -->
<!--   ggtitle('Meta-Analysis of Variance (Using Subsetting)') -->

**Thirdly**, although not previously done extensively, it seems that the best way to conduct this analysis is not through subsetting but through utilising model predictions as we did with Hedges' g previously, that way we retain the same methodology in model structure and test the same hypotheses. This can be done be utilising the same predict function but for lnCVR and var.lnCVR.

@@

```{r, warning=FALSE}
#Now try with multilevel model 
variance.model <- rma.mv(lnCVr, var.lnCVr, mods = ~ 1 + Sex*Environment, 
                          random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                         method = "REML", data = prelim.data2)
summary(variance.model)
```
<br></br>
**Fourthly**, we can plot predictions of lnCVR for various moderators:

```{r, fig.height= 6, fig.width=6, warning = FALSE}

>>>>

```{r, warning=FALSE, message=FALSE, results='hide'}
library(pander)
library(tidyr)
library(compute.es)
library(metafor)
library(plyr)
library(dplyr)
library(lme4)
library(forestplot)
library(ggplot2)
library(ggthemes)
library(kableExtra)
library(ggrepel)
library(reshape2)
library(RColorBrewer)
library(ggridges)
library(rstan) #Note that installation requires some effort
library(brms) 
library(backports) #seems to be a dependency
library(bayesplot)
#devtools::install_github("mvuorre/brmstools")
library(brmstools) 
source("Vdodge_function.R") # nice function for ggplot
```

@@

Outcome_and_sex %>% pander(split.cell = 40, split.table = Inf)
```
<br></br>

@@

```{r, fig.height=18, fig.width=12}

@@

# define upper and lower bounds
prelim.data$lowerci <- prelim.data$g - 1.96*(sqrt(prelim.data$var.g))
prelim.data$upperci <- prelim.data$g + 1.96*(sqrt(prelim.data$var.g))

library(ggthemes)
#Generate a plot
p.meta <- prelim.data %>% 
  mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female")) %>%

@@

@@

@@

@@

<input type=button class=hideshow></input>
```{r}
model.preliminary <- rma.mv(g, var.g, 
                         mods = ~ 1 + Sex * Environment + Taxon + Outcome.Class + log(Generations) + Blinding, # << ----- Add big model, then cull predictors to this one
                         random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                         method = "REML", 
                         data = prelim.data)

summary(model.preliminary)

#Also use bayesian model

brms.preliminary <- brm(g | se(SE)  ~ 1 + Sex * Environment + log(Generations) + Blinding 
                + (1|Study.ID) #group level effect #1
                + (1|Outcome)
                + (1|Taxon), 
                family = "gaussian", 
                seed = 1,
                cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
                control = list(adapt_delta = 0.999, max_treedepth = 15),
                data = prelim.data %>% mutate(SE = sqrt(var.g)))

#Plot model results
prelim.results.bayesplot <- bayesplot::mcmc_areas(posterior_samples(brms.preliminary)[,1:11]) + 
  geom_vline(xintercept = 0, linetype = 2)

prelim.results.bayesplot

@@

summary(model.complete)

#Have taxon as fixed effects
brms.complete <- brm(g | se(SE)  ~ 1 + Sex * Environment + Taxon
                + (1|Study.ID) #group level effect #1
                + (1|Outcome), #group level effect #2 
                family = "gaussian", 
                seed = 1,
                cores = 4, chains = 4, iter = 4000, # Run 4 chains in parallel for 4000 iterations (2000 are burn in)
                control = list(adapt_delta = 0.999, max_treedepth = 15),
                data = restricted.data %>% mutate(SE = sqrt(var.g)))

bayesplot::mcmc_areas(posterior_samples(brms.complete)[,1:13]) +
  geom_vline(xintercept = 0, linetype = 2)

# new.data <- restricted.data %>% 
#   mutate(SE = sqrt(var.g)) %>% 
#   select(Sex, Environment, Blinding, Generations, SE, Taxon) %>% 
#   mutate(Generations = mean(log(Generations)), 
#          Blinding = "Blind", 
#          Taxon = "Fly",
#          Outcome = "Reproductive Success",
#          SE = 0) %>% 
#   distinct() %>% arrange(Sex, Environment)
# predictions.complete <- data.frame(new.data, fitted(brms.complete, newdata = new.data, re_formula = NA))
# 
# pd <- position_dodge(0.2)
# predictions.complete %>% ggplot(aes(Sex, Estimate, group = Environment, colour = Environment)) + 
#   geom_errorbar(aes(ymin = X2.5.ile, ymax = X97.5.ile), position = pd, width = 0) +
#   geom_point(position = pd) +
#   coord_flip()
```

@@

We can run a bayesian model using the brms package. The model has the same moderators as the REML approach used above.

```{r, warning = FALSE, results='hide', message=FALSE}
#Use brm to create a model similar to the one used in the REML approach. 
meta.brms <- brm(g| se((SE), sigma = TRUE)  ~ 1 + Sex * Environment #response is Hedges' g and the standard error associated with it (SE), sex, environment and their interaction are moderators
                + (1|Study.ID) #group level effect #1
                + (1|Outcome), #group level effect #2 (unrelated/crossed) with #1
                family = "gaussian", #default
                seed = 1,
                cores = 4, chains = 4, iter = 4000, #Run 4 chains in parrallel for 4000 iterations (2000 are burn in)
                control = list(adapt_delta = 0.999, max_treedepth = 15),
                data = restricted.data %>% mutate(SE = sqrt(var.g)))

summary(meta.brms)

#You can obtain a posterior sampling through the ``fitted.brmsfit`` function, which gives the same posterior values as doing it manually (see below).**Note that the fitted values obtained here have much smaller error than the predict values, which blow out**

# #obtain average variance of each group in the prediction
# av.var.g <- as.numeric(c(restricted.data %>% filter (Sex == 'M' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
#               restricted.data %>% filter (Sex == 'B' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
#               restricted.data %>% filter (Sex == 'F' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
#               restricted.data %>% filter (Sex == 'M' & Environment == "Stressed") %>% summarise(mean = mean(var.g)),
#               restricted.data %>% filter (Sex == 'B' & Environment == "Stressed") %>% summarise(mean = mean(var.g)),
#               restricted.data %>% filter (Sex == 'F' & Environment == "Stressed") %>% summarise(mean = mean(var.g))))

#Expand grid for environment and sex
# brms.newdata <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
#                            Environment = c("Unstressed", "Stressed")))
# #Add variance
# brms.newdata$var.g <- av.var.g
# 
# #Add predictions
# brms.predict <- fitted(meta.brms, newdata = brms.newdata, re_formula = NA)
# brms.predict <- as.data.frame(brms.predict)
# brms.predictions <- data.frame(brms.newdata$Sex, brms.newdata$Environment, brms.predict$Estimate, brms.predict$Est.Error, brms.predict$Q2.5, brms.predict$Q97.5)
# 
# #Name columns
# colnames(brms.predictions) <- c("Sex", "Environment", "Estimate", "Error", "LCI", "UCI", "n")
```

@@

```{r}
post <- (posterior_samples(meta.brms, 
                           pars = c("b_Intercept", "b_SexB", "b_SexF", 
                                    "b_EnvironmentStressed", "b_SexB:EnvironmentStressed", 
                                    "b_SexF:EnvironmentStressed")) %>%
         mutate(both_benign = b_Intercept + b_SexB,
         both_stressful = b_Intercept + b_SexB + b_EnvironmentStressed + `b_SexB:EnvironmentStressed`,
         male_benign = b_Intercept,
         male_stressful = b_Intercept + b_EnvironmentStressed,
         female_benign = b_Intercept + b_SexF,
         female_stressful = b_Intercept + b_SexF + b_EnvironmentStressed + `b_SexF:EnvironmentStressed`))[,-(1:6)]

#Obtain posterior fitted values and transform
# posterior_fit <- data.frame(t(posterior_linpred(meta.brms, newdata = brms.newdata, re_formula = NA)))

#Add columns for Environment and Sex
post <- as.data.frame(t(post))
post$Sex <- c("Both", "Both", "Male", "Male", "Female", "Female")
post$Environment <- c("Benign", "Stressful", "Benign", "Stressful", "Benign", "Stressful")

#Clean up dataframe
post <- melt(post, id = c("Sex", "Environment"))
post$variable <- NULL
```

@@

pd <- position_dodgev(height = 0.3)
posterior.plot <- post %>% ggplot()+
  stat_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.4, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F, quantile_lines = T, quantiles = 2)+
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
    ylab("Environment")+
  xlab("\nEffect Size (Hedges' g)")+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")+
  scale_x_continuous(limits = c(-0.5, 1.2), breaks = c(-1, -.5, 0, 0.5, 1))+

@@

# svg("figures/both_plot.svg", width=6, height=6)
# both.plots
# dev.off()
# 
# pdf("figures/both_plot.pdf",  width = 5.5, height = 5.5)
# both.plots
# dev.off()
```
<br></br>
**Figure X** Posterior fitted values for Hedges' g alongside the predictions from metafor

@@

@@

```{r}
#Calculate lnCVr and var.lnCVr
#for lnCVR
restricted.data$lnCVr <- Calc.lnCVR(restricted.data$mean.low, restricted.data$sd.low, restricted.data$n.low, restricted.data$mean.high, restricted.data$sd.high, restricted.data$n.high)

#for variance in lnCVR
restricted.data$var.lnCVr <- Calc.var.lnCVR(restricted.data$mean.low, restricted.data$sd.low, restricted.data$n.low, restricted.data$mean.high, restricted.data$sd.high, restricted.data$n.high, Equal.E.C.Corr=F)

restricted.data <- restricted.data %>% drop_na(lnCVr)
```

**Thirdly**, although not previously done extensively, it seems that the best way to conduct this analysis is not through subsetting but through utilising model predictions as we did with Hedges' g previously, that way we retain the same methodology in model structure and test the same hypotheses. This can be done be utilising the same predict function but for lnCVR and var.lnCVR. For the brms model we can obtain predictions manually or through the ``fitted.brmsfit``.

@@

```{r, warning=FALSE}
#Now try with multilevel model 
variance.model <- rma.mv(lnCVr, var.lnCVr, mods = ~ 1 + Sex*Environment, 
                          random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                         method = "REML", data = restricted.data)
summary(variance.model)

#Now with brms
